A Type System for Safe and Scalable Parallelism using Logical Regions

### 2012-07-10 doc/popl2013/intro.tex
Updating circuit example in the intro to fix some bugs

-- Simulation initialization and invocation
function simulate_circuit[rl,rw,rn] ( all_nodes : node_list<rl,rn>@rl, 
      all_wires : wire_list<rl,rw,rn,rn>@rl, steps : int ), 
      reads(rn,rw,rl), writes(rn,rw,rl) : bool = 
  let pc : <coloring(rn),coloring(rn),coloring(rw)> 
            = color_circuit[rn,rw,rl](all_nodes,all_wires) in
  -- Disjoint partition for the owned nodes of each piece
  partition rn using pc.1 as rn0,rn1 in
  -- Aliased partition for ghost nodes of each piece
  partition rn using pc.2 as rg0,rg1 in
  -- Disjoint partition for the owned wires of each piece
  partition rw using pc.3 as rw0,rw1 in
  let piece0 : CircuitPiece<rl,rw,rn> = 
                build_piece[rl,rw,rn,rw0,rn0,rg0](all_nodes,all_wires,pc.1,pc.2,pc.3,0) in
  let piece1 : CircuitPiece<rl,rw,rn> = 
                build_piece[rl,rw,rn,rw1,rn1,rg1](all_nodes,all_wires,pc.1,pc.2,pc.3,1) in
      execute_time_steps[rl,rw,rn](piece0,piece1,steps)

@@

function build_lists[rl,rw,rn,rpw,rpn,rg] ( nodes : node_list<rl,rn>@rl, 
       wires : wire_list<rl,rw,rn>@rl, oc : coloring(rn), gc : multicoloring(rn), 
       wc : coloring(rw), c : int), reads(rn,rw,rl), writes(rl) 
       : < wire_list<rl,rpw,rpn,rg>@rl, node_list<rl,rpn>@rl > = 
  -- Construct lists of node and wire pointers for the given colorings

function build_piece[rl,rw,rn,rpw,rpn,rg] ( nodes : node_list<rl,rn>@rl, 
      wires : wire_list<rl,rw,rn>@rl, oc : multicoloring(rn), gc : coloring(rn), 
      wc : coloring(rw), c : int), reads(rn,rw,rl), writes(rl) : CircuitPiece<rl,rw,rn> =
  let piece_lists : < wire_list<rl,rpw,rpn,rg>@rl, node_list<rl,rpn>@rl > = 
    build_lists[rl,rw,rn,rpw,rpn,rg](nodes,wires,oc,gc,wc,c) in
      pack piece_lists as CircuitPiece<rl,rw,rn>[rpw,rpn,rg] 
\end{lstlisting}

>>>>

-- Simulation initialization and invocation
function simulate_circuit[rl,rw,rn] ( all_nodes : node_list<rl,rn>@rl, 
                            all_wires : wire_list<rl,rw,rn,rn>@rl, steps : int ), 
      reads(rn,rw,rl), writes(rn,rw,rl) : bool = 
  let pc : <coloring(rn),multicoloring(rn),coloring(rw)> 
            = color_circuit[rn,rw,rl](all_nodes,all_wires) in
  -- Disjoint partition for the owned nodes of each piece
  partition rn using pc.1 as rn0,rn1 in
  -- Aliased partition for ghost nodes of each piece
  partition rn using pc.2 as rg0,rg1 in
  -- Disjoint partition for the owned wires of each piece
  partition rw using pc.3 as rw0,rw1 in
  let lists0 : <wire_list<rl,rw0,rn0,rg0>@rl,node_list<rl,rn0>@rl> = 
        build_lists[rl,rw,rn,rw0,rn0,rg0](all_nodes,all_wires,pc.1,pc.2,pc.3,0) in
  let piece0 : CircuitPiece<rl,rw,rn> = 
        pack lists0 as CircuitPiece<rl,rw,rn>[rw0,rn0,rg0] in
  let lists1 : <wire_list<rl,rw1,rn1,rg1>@rl,node_list<rl,rn1>@rl> =
        build_lists[rl,rw,rn,rw1,rn1,rg1](all_nodes,all_wires,pc.1,pc.2,pc.3,1) in
  let piece1 : CircuitPiece<rl,rw,rn> = 
        pack lists1 as CircuitPiece<rl,rw,rn>[rw1,rn1,rg1] in
      execute_time_steps[rl,rw,rn](piece0,piece1,steps)

@@

function build_lists[rl,rw,rn,rpw,rpn,rg] ( nodes : node_list<rl,rn>@rl, 
       wires : wire_list<rl,rw,rn>@rl, oc : coloring(rn), gc : multicoloring(rn), 
       wc : coloring(rw), c : int), reads(rn,rw,rl), writes(rl) 
       : < wire_list<rl,rpw,rpn,rg>@rl, node_list<rl,rpn>@rl > = 
  -- Construct lists of node and wire pointers for the given colorings
\end{lstlisting}
